Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-24 papers/BON_VHDL/paper.tex
minor again
minor corrections

\subsection{Contracting}
\emph{Contracting} is the definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, analog kernel calculate quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We will agree that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any loop equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined pre/post condition trought input/output 
parameters and theirs constraints. Furthermore any subtype/subnature 
represents restricted set of values from a base type/nature. 
The condition that determines which values are in the subtype/subnature,  
may be contracted by specifying characteristic predicate. 
For example, in typed $\lambda$ calculi, the VHDL-AMS subtype \lstinlinenc|bit| of 
\lstinlinenc|integer|, may be defined as \texttt{bit:=$\lambda$ n:nat.n < 2}. 
The corresponding informal and formal BON transformation looks like:
\input{bitbon}
Therefore as an notition based on contract design, and as  methodology of 
best modelling practices, BON is the obvious choice for the our simulator.
Throughout this paper we will try to make this more clearly.

>>>>

\subsection{Contracting}
\emph{Contracting} is the definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, analog kernel calculate quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We will agree that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any loop equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined pre(post) condition trought input(output) 
parameters and theirs constraints. Furthermore any subtype(subnature) 
represents restricted set of values from a base type(nature). 
The condition that determines which values are in the subtype(subnature)  
may be contracted by specifying characteristic predicate. 
For example, in typed $\lambda$ calculi, the VHDL-AMS subtype \lstinlinenc|bit| of 
\lstinlinenc|integer|, may be defined as \texttt{bit:=$\lambda$ n:nat.n < 2}. 
The corresponding informal and formal BON transformations are shown 
by the example below:
\input{bitbon}
Therefore as an notition based on contract design, and as  methodology of 
best modelling practices, BON is the obvious choice for the our simulator.
Throughout this paper we will try to make this more clearly.
